---
title: "Aerial Survey Models for 2011 Shrimp data"
author: "Kevin M. Purcell"
date: "Monday, August 11, 2014"
output: html_document
---


```{r envSetup}
graphics.off()
rm(list=ls(all=TRUE))

library(dplyr)
library(maptools)
library(maps)
library(mapdata)
library(stargazer)

```


```{r dataInput}
#dat <- read.csv("W://Craig//AerialSurvey//analysis//grid_AS_data_2011.csv")
dat <- read.csv("W://Craig//AerialSurvey//analysis//AS_data_gridv3.csv")
dist <- read.csv("W://Craig//AerialSurvey//analysis//distShorlineData_KC.csv")
pnts <- read.csv("W://Craig//AerialSurvey//analysis//grid_v3.csv")

names(dat)
#str(dat)
summary(dat)
names(dist)

summary(pnts)
pnts <- subset(pnts, pnts$cent_y>=28.26&pnts$cent_y<=29.59)
dat <- subset(dat, dat$cent_y>=28.26&dat$cent_y<=29.59)
names(dat)
names(pnts)

```



```{r dataMungin}
agg_pnts <- dplyr::select(dat, centroidID, cent_x, cent_y)
agg_pnts$count <- 1
agg.dat <- aggregate(count ~ centroidID, data=agg_pnts, FUN=sum)
agg.dat <- merge(agg_pnts, pnts, by=c("cent_x", "cent_y"), all.y=T)

#agg.dat <- subset(agg.dat, agg.dat$y > 0)
plot(agg.dat$cent_y ~ agg.dat$cent_x)
map("state",fill=T,col="gray",add=T)

summary(agg.dat)
agg.dat[ is.na(agg.dat) ] <- 0 
summary(agg.dat)


dat <- merge(dat, dist, by=c("a_lat","a_lon","Identifyin"))
agg_env <- dplyr::select(dat, centroidID, cent_x, cent_y, oxy, salt, temp, cdom, chloro, dist_shore)
agg.env <- aggregate(cbind(oxy, salt, temp, cdom, chloro, dist_shore) ~ centroidID + cent_x + cent_y, data=agg_env, FUN=mean)


gam.dat <- merge(agg.dat, agg.env, by=c("centroidID", "cent_x", "cent_y"), all.x=T)
gam.dat <- dplyr::select(gam.dat, -centroidID, -id)
summary(gam.dat)


```

```{r gamModel}
library(mgcv)

#gam.dat <- na.omit(gam.dat$oxy)

mod.1<-gam(count ~ s(oxy) + s(dist_shore), family=binomial("logit"), data=gam.dat)

gam.check(mod.1)

summary(mod.1)
plot.gam(mod.1)




```

No real effects using a general model of just the environmental factors.  However, a spatial model will not run due to limited data.  So I will strip down the model based on this initial run and attempt a spatial model. 


```{r, results='asis'}

mod.2<-gam(log(count) ~ s(x,y) + s(oxy)
             , family=poisson, data=gam.dat)

gam.check(mod.2)

summary(mod.2)
plot.gam(mod.2, select=1, resid=T)
map("state",fill=T,col="gray",add=T)

vis.gam(mod.2, view=c("x", "y"), 
        plot.type="contour", type="response", contour="black",
        color="topo",
        main="", ylab="Latitude", xlab="Longitude")


# add coastline
map("worldHires", fill=T, col="grey",add=T)
```

The zero contour line transits the coast from the western bank of the Atchafalya to south east.  Next model looks at accounting for east or west within the model.


```{r longMod}

gam.dat$region <- 1
gam.dat$region[gam.dat$x <= (-91.054)]=1
gam.dat$region[gam.dat$x > (-91.054)]=2
head(gam.dat)
summary(gam.dat)
str(gam.dat$region)
gam.dat <- subset(gam.dat, gam.dat$dist_shore<125)

mod.3<-gam(log(count) ~  s(oxy) + factor(region)
             , family=poisson, data=gam.dat)

gam.check(mod.3)

summary(mod.3)
plot.gam(mod.3, shade=T)
plot.gam(mod.3, all.terms = T)
```


```{r eastMod}

east.dat <- subset(gam.dat, gam.dat$region == 2)
mod.4 <- gam(log(count) ~ s(oxy) + s(dist_shore), family=poisson, data=east.dat)
gam.check(mod.4)
plot.gam(mod.4, shade=T)

summary(mod.4)

west.dat <- subset(gam.dat, gam.dat$region == 1)

mod.5 <- gam(log(count) ~ s(oxy) + s(dist_shore), family=poisson, data=west.dat)
summary(mod.5)
plot.gam(mod.5, shade=T)

```


```{r modComp }
par(mfrow=c(1,2))
vis.gam(mod.5, main="Western Louisiana", 
        theta=35, phi=30,
        ticktype="detailed",
        zlab="Trawler Density",
        ylab="Distance from Shore",
        xlab="Oxygen",
        cex=0.5)
vis.gam(mod.4, main="Eastern Louisiana", 
        theta=35, phi=30,
        ticktype="detailed",
        zlab="Trawler Density",
        ylab="Distance from Shore",
        xlab="Oxygen",
        cex=0.5)


```


## Kernal Density Plot

I am considering using a different analysis approach for the aerial survey data due to the loss of sample size when scaling the points up to bins.  Today I am going to try to create kernal density plots based on a [blog post](http://www.samuelbosch.com/2014/02/creating-kernel-density-estimate-map-in.html) by [Samuel Bosch](http://www.samuelbosch.com) or [@gissolved](https://twitter.com/gissolved) on twitter.  

```{r kernalDensity, echo=TRUE, warning=FALSE, message=FALSE}

library("KernSmooth")
library("raster")

input <- read.csv("W://Craig//AerialSurvey//GIS//AS_2011_data.csv")
names(input) #find coordinate locations

output <- "shrimp_vessel_density.asc"

coordinates <- input[,4:5] #get coordinates

est <- KernSmooth::bkde2D(coordinates,
                          bandwidth=c(3,3))
est$fhat[est$fhat<0.00001] <- 0 ## ignore very small values
contour(est$x2, est$x1, est$fhat)                          

plot(input$a_Latitude ~ input$a_Longitude)
map("state",fill=T,col="gray",add=T)

# create raster
est.raster = raster(list(x=est$x2,y=est$x1,z=est$fhat))
projection(est.raster) <- CRS("+init=epsg:4326")
#xmin(est.raster) <- -180
#xmax(est.raster) <- 180
#ymin(est.raster) <- -90
#ymax(est.raster) <- 90
# visually inspect the raster output
plot(est.raster)
# write an ascii file
#writeRaster(est.raster,output,"ascii")
```

This plot looks unremarkable and I have to assume that something is not coming out correctly.  It may have something to do with the scale of the analysis or